D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-08 ootavacuous.tex
Wordsmith the tooling section
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Some other tools respond to complexity by consuming all available CPU
and memory, which can also be interpreted as a good and sufficient
warning message.

However, there is an important special case for tools that are closely
associated with a C++ implementation.
Such tools can simply use that implementation's classification of
dependencies as semantic on the one hand or non-semantic on the other.
While taking this approach sacrifices significant generality, it has
the not insignificant benefit of greatly reducing the cost of dependency
analysis, potentially all the way to zero.

>>>>

One advantage that tools often have over C++ implementations is the
ability to devote much more computational power to the problem at hand.
In fact, some tools respond to excessive complexity by consuming all
available CPU and memory, which can also be interpreted as a good and
sufficient warning message.

However, there is an important special case for tools that are closely
associated with a C++ implementation.
Such tools can simply use that implementation's classification of
dependencies as semantic on the one hand or non-semantic on the other.
While taking this approach sacrifices significant generality, it has the
significant benefit of greatly reducing the cost of dependency analysis,
potentially all the way down to zero.
